### 2025-03-06 paper/preprint/paper.tex
ok final final runs?

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, titlerule=0mm, coltitle=black, left=2mm, bottomtitle=1mm, breakable, opacityback=0, rightrule=.15mm, toptitle=1mm, arc=.35mm, bottomrule=.15mm, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6]

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{41.9}} & \color{green}{\textbf{8.13}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{28.9}} & \color{green}{\textbf{2.28}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{10.9}} & \color{green}{\textbf{7.47}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{22.3}} & \color{green}{\textbf{4.87}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{30.7}} & \color{green}{\textbf{5.77}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{17.1}} & \color{green}{\textbf{7.98}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{5}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{35.7}} & \color{green}{\textbf{7.56}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{37}} & \color{green}{\textbf{5.31}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{35.5}} & \color{green}{\textbf{4.27}} \\

@@

  \color{red}{\textbf{0.75}} & \color{red}{\textbf{0.5}} & \color{red}{\textbf{5}} & \color{red}{\textbf{ECCo}} & \color{red}{\textbf{-0.94}} & \color{red}{\textbf{17.6}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{32.3}} & \color{green}{\textbf{3.49}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{28.3}} & \color{green}{\textbf{5.05}} \\

@@

  \color{red}{\textbf{0.9}} & \color{red}{\textbf{0.5}} & \color{red}{\textbf{5}} & \color{red}{\textbf{Generic}} & \color{red}{\textbf{-0.0952}} & \color{red}{\textbf{17.1}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{39.1}} & \color{green}{\textbf{8.3}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{13.6}} & \color{green}{\textbf{12.8}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{4.57}} & \color{green}{\textbf{5.88}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{19.1}} & \color{green}{\textbf{4.43}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{24.8}} & \color{green}{\textbf{4.78}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{5}} & \color{green}{\textbf{5}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{37}} & \color{green}{\textbf{9.21}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{21.8}} & \color{green}{\textbf{5.97}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{8.56}} & \color{green}{\textbf{13.6}} \\

@@

  \color{red}{\textbf{0.9}} & \color{red}{\textbf{5}} & \color{red}{\textbf{5}} & \color{red}{\textbf{Generic}} & \color{red}{\textbf{-1.18}} & \color{red}{\textbf{16.7}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{21.9}} & \color{green}{\textbf{7.48}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{30.8}} & \color{green}{\textbf{10.7}} \\

@@

  \color{red}{\textbf{0.95}} & \color{red}{\textbf{5}} & \color{red}{\textbf{5}} & \color{red}{\textbf{ECCo}} & \color{red}{\textbf{-5.29}} & \color{red}{\textbf{24.5}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{26.9}} & \color{green}{\textbf{4.08}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{16.6}} & \color{green}{\textbf{4.3}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{10}} & \color{green}{\textbf{5}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{2.47}} & \color{green}{\textbf{8.57}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{10}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{29.9}} & \color{green}{\textbf{15.8}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{10}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{15.2}} & \color{green}{\textbf{10.2}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{10}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{6.88}} & \color{green}{\textbf{5.11}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{10}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{34.7}} & \color{green}{\textbf{9.74}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{10}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{35}} & \color{green}{\textbf{7.11}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{10}} & \color{green}{\textbf{5}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{35.7}} & \color{green}{\textbf{3.83}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{10}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{33}} & \color{green}{\textbf{6.45}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{10}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{8.07}} & \color{green}{\textbf{7.68}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{20}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{12.6}} & \color{green}{\textbf{17.6}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{20}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{17.2}} & \color{green}{\textbf{4.25}} \\

@@

  \color{green}{\textbf{0.75}} & \color{green}{\textbf{20}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{15.6}} & \color{green}{\textbf{8.38}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{20}} & \color{green}{\textbf{5}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{26.3}} & \color{green}{\textbf{6.62}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{20}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{39}} & \color{green}{\textbf{5.98}} \\

@@

  \color{green}{\textbf{0.9}} & \color{green}{\textbf{20}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{15.1}} & \color{green}{\textbf{7.46}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{20}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{7.23}} & \color{green}{\textbf{4.74}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{20}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{19.3}} & \color{green}{\textbf{14.6}} \\

@@

  \color{green}{\textbf{0.95}} & \color{green}{\textbf{20}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{37.3}} & \color{green}{\textbf{7.78}} \\

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, opacitybacktitle=0.6, arc=.35mm, toptitle=1mm, leftrule=.75mm, colframe=quarto-callout-note-color-frame, colback=white, breakable, toprule=.15mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, colbacktitle=quarto-callout-note-color!10!white, rightrule=.15mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, titlerule=0mm, coltitle=black]

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{41.9}} & \color{Green}{\textbf{8.13}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{28.9}} & \color{Green}{\textbf{2.28}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{10.9}} & \color{Green}{\textbf{7.47}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{22.3}} & \color{Green}{\textbf{4.87}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{30.7}} & \color{Green}{\textbf{5.77}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{17.1}} & \color{Green}{\textbf{7.98}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{35.7}} & \color{Green}{\textbf{7.56}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{37}} & \color{Green}{\textbf{5.31}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{0.1}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{35.5}} & \color{Green}{\textbf{4.27}} \\

@@

  \color{Red}{\textbf{0.75}} & \color{Red}{\textbf{0.5}} & \color{Red}{\textbf{5}} & \color{Red}{\textbf{ECCo}} & \color{Red}{\textbf{-0.94}} & \color{Red}{\textbf{17.6}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{0.5}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{32.3}} & \color{Green}{\textbf{3.49}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{0.5}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{28.3}} & \color{Green}{\textbf{5.05}} \\

@@

  \color{Red}{\textbf{0.9}} & \color{Red}{\textbf{0.5}} & \color{Red}{\textbf{5}} & \color{Red}{\textbf{Generic}} & \color{Red}{\textbf{-0.0952}} & \color{Red}{\textbf{17.1}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{0.5}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{39.1}} & \color{Green}{\textbf{8.3}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{0.5}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{13.6}} & \color{Green}{\textbf{12.8}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{0.5}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{4.57}} & \color{Green}{\textbf{5.88}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{0.5}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{19.1}} & \color{Green}{\textbf{4.43}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{0.5}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{24.8}} & \color{Green}{\textbf{4.78}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{37}} & \color{Green}{\textbf{9.21}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{21.8}} & \color{Green}{\textbf{5.97}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{8.56}} & \color{Green}{\textbf{13.6}} \\

@@

  \color{Red}{\textbf{0.9}} & \color{Red}{\textbf{5}} & \color{Red}{\textbf{5}} & \color{Red}{\textbf{Generic}} & \color{Red}{\textbf{-1.18}} & \color{Red}{\textbf{16.7}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{21.9}} & \color{Green}{\textbf{7.48}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{30.8}} & \color{Green}{\textbf{10.7}} \\

@@

  \color{Red}{\textbf{0.95}} & \color{Red}{\textbf{5}} & \color{Red}{\textbf{5}} & \color{Red}{\textbf{ECCo}} & \color{Red}{\textbf{-5.29}} & \color{Red}{\textbf{24.5}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{26.9}} & \color{Green}{\textbf{4.08}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{16.6}} & \color{Green}{\textbf{4.3}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{2.47}} & \color{Green}{\textbf{8.57}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{29.9}} & \color{Green}{\textbf{15.8}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{15.2}} & \color{Green}{\textbf{10.2}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{6.88}} & \color{Green}{\textbf{5.11}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{34.7}} & \color{Green}{\textbf{9.74}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{35}} & \color{Green}{\textbf{7.11}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{35.7}} & \color{Green}{\textbf{3.83}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{33}} & \color{Green}{\textbf{6.45}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{10}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{8.07}} & \color{Green}{\textbf{7.68}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{12.6}} & \color{Green}{\textbf{17.6}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{17.2}} & \color{Green}{\textbf{4.25}} \\

@@

  \color{Green}{\textbf{0.75}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{15.6}} & \color{Green}{\textbf{8.38}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{26.3}} & \color{Green}{\textbf{6.62}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{39}} & \color{Green}{\textbf{5.98}} \\

@@

  \color{Green}{\textbf{0.9}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{15.1}} & \color{Green}{\textbf{7.46}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{5}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{7.23}} & \color{Green}{\textbf{4.74}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{25}} & \color{Green}{\textbf{ECCo}} & \color{Green}{\textbf{19.3}} & \color{Green}{\textbf{14.6}} \\

@@

  \color{Green}{\textbf{0.95}} & \color{Green}{\textbf{20}} & \color{Green}{\textbf{50}} & \color{Green}{\textbf{Generic}} & \color{Green}{\textbf{37.3}} & \color{Green}{\textbf{7.78}} \\

### 2025-03-06 paper/sections/abstract.qmd
ok final final runs?

Counterfactual Explanations have emerged as a popular tool to explain predictions made by opaque machine learning models: they explain how factual inputs need to change in order for some fitted model to produce some desired output. Much existing research has focused on identifying explanations that are not only valid but also deemed desirable with respect to the underlying data and stakeholder requirements. Recent work has shown that under this premise, the task of learning desirable explanations is effectively reassigned from the model itself to the (post-hoc) counterfactual explainer. Building on that work, we propose a novel model objective that leverages counterfactuals during the training phase (ad-hoc) in order to minimize the divergence between learned representations and desirable explanations. Through extensive experiments, we demonstrate that our proposed methodology facilitates training models that inherently deliver desirable explanations while maintaining high predictive performance.

>>>>

We propose a novel model objective that leverages counterfactual explanations to increase the explanatory capacity of trained models. Counterfactual explanations have emerged as a popular tool to explain predictions made by opaque machine learning models: they inform how factual inputs would need to change in order for a model to produce some desired output. Much existing research has focused on generating counterfactuals that are not only valid but also deemed acceptable with respect to the stakeholder requirements and plausible with respect to the underlying data. Recent work has shown that under this premise, the task of learning plausible explanations---ones that respect the conditional distribution of the target class---is effectively reassigned from the model itself to the post-hoc counterfactual explainer. Building on that work, we propose a novel objective function that employs counterfactuals (ad-hoc) during the training phase to minimize the divergence between the learned representations and the explanations. Through extensive experiments, we demonstrate that our proposed method facilitates training models that deliver inherently plausible explanations while maintaining high predictive performance.
